Reading Notes

### 2020-08-11 1summ.tex
moved some of my notes into the bullets

A coarse graining pipeline will help make multi-scale simulations more accesible and useable for others. 
This can be useful for screening of potential OPV compounds.
<talk about VOTCA?>
<talk about TRUE simulations and reproducibility in the field>
<talk about our supercomputer allocations?>
<talk about what I've done already?>

IM - Potential to advance knowledge and understanding within own and across different fields
    - Activities explore creative, original, or potentially transformative concepts?
    - Plan well-reasoned, well organized, based on sound rationale?
    - Mechanism to assess success?
    - How qualified is team?
    - Adequate resources to carry out activities?

@@

Helping to make research transferrable, reproducible, useable, and extensible. 
Wriitng tutorials and documentation while keep in mind principles of oftware carpentry instructor training. 
Using software dev best practices to be efficient and make sure that I'm not making code for someone else to struggle through later. 
Training/teaching undergrads.
Working as part of a team.

BI - Potential to benefit society, contribute to achievement of desired societal outcomes
    - Activities explore creative, original, or potentially transformative concepts?
    - Plan well-reasoned, well organized, based on sound rationale?
    - Mechanism to assess success?
    - How qualified is team?
    - Adequate resources to carry out activities?

>>>>

IM - Potential to advance knowledge and understanding within own and across different fields
- Activities explore creative, original, or potentially transformative concepts?
A coarse graining pipeline will help make multi-scale simulations more accesible and useable for others. 
This can be useful for screening of potential OPV compounds.

- Plan well-reasoned, well organized, based on sound rationale?

- Mechanism to assess success?
<comparing mobilities, diffraction to experiment>

- How qualified is team?
<talk about what I've done already?>

- Adequate resources to carry out activities?
<talk about our supercomputer allocations?>

@@

BI - Potential to benefit society, contribute to achievement of desired societal outcomes
- Activities explore creative, original, or potentially transformative concepts?
<talk about VOTCA?>
<talk about TRUE simulations and reproducibility in the field>

- Plan well-reasoned, well organized, based on sound rationale?

- Mechanism to assess success?
a sign of well-written, understandable code is if other people use it. 
It's tricky because this is completely out of my control, but if other people find my code useful--it is a success.
by integrating what I do with other existing codebases I can help to achieve this goal.
Also having good tutorials and documentation.

- How qualified is team?
Helping to make research transferrable, reproducible, useable, and extensible. 
Writing tutorials and documentation while keep in mind principles of oftware carpentry instructor training. 
Using software dev best practices to be efficient and make sure that I'm not making code for someone else to struggle through later. 
Training/teaching undergrads.
Working as part of a team.

- Adequate resources to carry out activities?
oss community
software carpentry training
experience with teaching/training undergrads
